Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-09 ms.tex
cooling/conduction

In addition to our standard set of solutions neglecting thermal conduction and cooling, we explore a few test simulations including these effects, as marked in Table \ref{table:models}.  {\bf BDM: EXPAND!!!!  Explain that they don't matter.}

@@

Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating
source (stars, MSPs, SNe Ia, and black hole feedback) calculated for
the average star formation history of galaxies containing a given
black hole mass.  Again, Ia heating is suppressed in low mass galaxies
because the Ia radius exceeds the nominal stagnation radius (bottom
panel).  MSP heating is again found to be negligible for all black
hole masses.  The younger stellar populations characterizing galaxies
with $\Mbh\lsim 5\times 10^{8} \Msun$ are dominated by stellar wind
and Ia heating, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and
$v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.  Only for the most
massive galaxies, with $\Mbh\gsim 5\times 10^{8} \Msun$, does the lack
of young stellar populations significantly reduce the role of stellar
wind
heating.  %Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
Strikingly, {\it we find that galactic nuclei experiencing the same
  average star formation history as their host galaxies produce
  thermally stable flows across almost all black hole masses}.  One exception may occur for the highest mass black holes, for which the total heating velocity is comparable to the stellar velocity dispersion and thermal stability for the average star formation history is marginal ($\S\ref{sec:mdot}$).

>>>>

In addition to our standard set of solutions neglecting thermal
conduction and cooling, we explore a few test simulations including
these effects, as marked in Table \ref{table:models}. For solutions we
with large wind heating parameters ($\vwO \gsim 1200 km/s$ km/s), we
expect radiative cooling to have virtually no effect on the solution
for reasonable values of the mass return parameter.  For cusp galaxies
Thermally stable solutions are possible for values of the wind heating
parameter as low as $\vwO=300$ km/s. However, this will be dependent
on the value of the mass return parameter (and thus on the age of the
stellar population) and on the break radius, $\rb$. For $\vwO\simeq
300$ km/s, solutions with large $\rb$ will have large stagnation radii
and thus larger densities. Thus, solution with $v_w$=300 km/s
$\rb\gsim 100$ pc, would be thermally unstable.  The picture is
qualitatively similar for core galaxies. However, the stagnation
radius ``runs away'' to large radii at much smaller values of the wind
heating paramter ($\vwO\simeq 600 km/s$). Thus, thermal instability
sets in for higher values of $\vwO$ for core galaxies.

In practice we expect that the effective wind heating will
be or order $\sim 1000$ km/s if heating is dominated by young
stars as would be the case for small black holes. This region of
parameter space should be thermally stable. For higher mass
black holes heating would be dominated by the supernovae and black
hole feedback and would be comparable to the stellar velocity
dispersion of the galaxy. Since core galaxies dominate for large
$\Mbh$ we expect this region of parameter space to be thermally unstable.

From our analytic results (see equation~\eqref{eq:conduction}) and
direct numerical experiments, we expect that thermal conduction would
introduce at most order unity changes in our solutions. The conductive
heating flux saturates, so that at the stagnation radius the
conductive heating rate is comparable to the external heating rate.

@@

Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating
source (stars, MSPs, SNe Ia, and black hole feedback) calculated for
the average star formation history of galaxies containing a given
black hole mass.  Again, Ia heating is suppressed in low mass galaxies
because the Ia radius exceeds the nominal stagnation radius (bottom
panel).  MSP heating is again found to be negligible for all black
hole masses.  The younger stellar populations characterizing galaxies
with $\Mbh\lsim 5\times 10^{8} \Msun$ are dominated by stellar wind
and Ia heating, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and
$v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.  Only for the most
massive galaxies, with $\Mbh\gsim 5\times 10^{8} \Msun$, does the lack
of young stellar populations significantly reduce the role of stellar
wind
heating.  %Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
Strikingly, {\it we find that galactic nuclei experiencing the same
  average star formation history as their host galaxies produce
  thermally stable flows across almost all black hole masses}.  One exception may occur for the highest mass black holes, for which the total heating velocity is comparable to the stellar velocity dispersion and thermal stability for the average star formation history is marginal ($\S\ref{sec:mdot}$).
{\bf AG: I wouldn't put too much stock in this since for higher masses
vw is comparable to sigma, and thus rs should run away to large
radii. This is especially true for core galaxies.}
